Hydraulic bore interaction with a column - A comparison between the solution of the shallow equation and experimental results

### 2015-03-13 doc/paper/paper.tex
Added Rankine-Hugoniot cond part

In all cases below, all boundary conditions are set to reflecting walls. 
\section{Dam Break}\label{Sec:Zero}
The initial condition for this and the following cases is given by
\eqm
h_0(x,y)=& 
\begin{cases}
0.25 & x<5.9 \\
0.02 & \text{otherwise}
\end{cases}\\
u_0(x,y) =& 0
\enm
In this comparison we will include results from OpenFOAM, an open source CFD software modeling air and water using the Navier-Stokes equations with turbulence model.
\par
Figure \ref{fig:waveheight_nocolumn} shows the time history of the wave height, measured at the center location where the column will be mounted in the following cases. 
The result from GeoClaw agrees quite well in general. 
If we zoom in Figure \ref{fig:waveheight_nocolumn} for smaller time range from $t=3s$ to $t=4s$, we get Figure \ref{fig:waveheight_nocolumn_zoomin}.
In Figure \ref{fig:waveheight_nocolumn_zoomin}, GeoClaw accurately predicted the arrival of the shock at t=3.8s. The arrival time of peak predicted by GeoClaw is almost the same as that from experiment (only about 0.02 second earlier).  
GeoClaw overestimates the peak water level a little, while OpenFOAM gives a better value.
At a later time, the wave gets reflected at the right wall of the tank, which can be seen by the second jump in wave height. 
GeoClaw also predicts the arrival time for this peak quite well, but overestimates the peak value by a small amount.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_nocolumn}
        \caption{time from 0 to 18}
        \label{fig:waveheight_nocolumn}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_nocolumn_zoomin}
        \caption{time from 3 to 4}
        \label{fig:waveheight_nocolumn_zoomin}
    \end{subfigure}
    \caption{time history of wave height for case without a column. }
\end{figure}

>>>>

In all cases below, all boundary conditions are set to reflecting walls. 
\section{Dam Break}\label{Sec:Zero}
The initial condition for this and the following cases is given by
\eqm
h_0(x,y)=& 
\begin{cases}
0.25 & x<5.9 \label{eq:init1}\\
0.02 & \text{otherwise}
\end{cases}\\
u_0(x,y) =& 0\label{eq:init2}
\enm
In this comparison we will include results from OpenFOAM, an open source CFD software modeling air and water using the Navier-Stokes equations with turbulence model.
\par
If we analyze the Rankine-Hugoniot condition of the initial conditions (\ref{eq:init1}) and (\ref{eq:init2}) for the shallow water equations:
\eqm
s(h_*-h) &=& h_*u_* - hu\\
s(h_*u_*-hu) &=& hu_*^2-hu^2 +\frac{1}{2}g(h_*^2-h^2)
\enm
we see that we can not find a $s$ that satisfies both equations, since $u$ and $u*$ are zero. This means the Rankine-Hugoniot condition is not satisfied and we expect a right and left going wave originating form the dam break.
Figure \ref{fig:waveheight_nocolumn} shows the time history of the wave height, measured at the center location where the column will be mounted in the following cases. 
The result from GeoClaw agrees quite well in general. 
If we zoom in Figure \ref{fig:waveheight_nocolumn} for smaller time range from $t=3s$ to $t=4s$, we get Figure \ref{fig:waveheight_nocolumn_zoomin}.
In Figure \ref{fig:waveheight_nocolumn_zoomin}, GeoClaw accurately predicted the arrival of the shock at t=3.8s. The arrival time of peak predicted by GeoClaw is almost the same as that from experiment (only about 0.02 second earlier).  
GeoClaw overestimates the peak water level a little, while OpenFOAM gives a better value.
At a later time, the wave gets reflected at the right wall of the tank, which can be seen by the second jump in wave height. 
GeoClaw also predicts the arrival time for this peak quite well, but overestimates the peak value by a small amount.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_nocolumn}
        \caption{time from 0 to 18}
        \label{fig:waveheight_nocolumn}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_nocolumn_zoomin}
        \caption{time from 3 to 4}
        \label{fig:waveheight_nocolumn_zoomin}
    \end{subfigure}
    \caption{time history of wave height for case without a column. }
\end{figure}
